---
title: "Association Between Universal Face Shield in a Quaternary Care Center and Reduction of SARS-COV2 Infections Among Healthcare Personnel and Hospitalized Patients"
author: "Vagish Hemmige and Kristen Panthagani"
date: "1/1/2021"
output:
  word_document: default
  pdf_document: default
  html_document: default
---


```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)
#setwd here
```

```{r library}
#code used for the analysis in:
#Mayar Al Mohajer, Kristen M. Panthagani, Todd Lasco, Bradley Lembcke, Vagish Hemmige,
#Association Between Universal Face Shield in a Quaternary Care Center and Reduction of SARS-COV2 Infections Among Healthcare Personnel and Hospitalized Patients, International Journal of Infectious Diseases, 2021,ISSN 1201-9712,
#https://doi.org/10.1016/j.ijid.2021.02.060.
#(https://www.sciencedirect.com/science/article/pii/S1201971221001466)

#Abstract: We implemented universal face shield for all healthcare personnel upon entry to facility in order to counter an increase in SARS-COV2 cases among healthcare personnel and hospitalized patients. There was a marked reduction of infections in both healthcare personnel and hospitalized patients between pre and post interventions. Our results support the universal face shield use as a part of multifaceted approach in areas of high SARS-COV2 community transmission.


#We import the R analyises necessary for the paper
library(dplyr)
library(readxl)
library(epitools)
library(ggplot2)
library(cowplot)
library(gtsummary)
library(flextable)

library(readr)
library(knitr)
library(reshape2)
library(dplyr)
library(ggplot2)
library(scales)
library(ggthemr)
library(svglite)

```


The following code imports the hospital data from Excel, then calculates the appropriate rates and confidence intervals for proportion of tests positive (based on the binomial model) as well as HAi rate (based on the poisson model).

```{r import}

Surveillance_manuscript2_9_19 <- read_excel("Surveillance manuscript2 9-19.xlsx")

#Set location of vertical line, which divides pre-intervention and post-intervention phases
Vertline<-12.9999

##Calculate exact binomial proportions with CIs and add to data set
Surveillance_manuscript2_9_19<-binom.exact(Surveillance_manuscript2_9_19$Positives, Surveillance_manuscript2_9_19$Tested) %>% 
  select(proportion, lower, upper) %>% 
  mutate(percentagemean=100*proportion, percentagelb=100*lower, percentageub=100*upper) %>% 
  select(percentagemean, percentagelb, percentageub) %>%
  cbind(Surveillance_manuscript2_9_19,.)

##calculate exact poisson rates with CIs and and add to data set
Surveillance_manuscript2_9_19<-pois.exact(Surveillance_manuscript2_9_19$HAI, Surveillance_manuscript2_9_19$Ptdays)%>%
  mutate(HAIrate=1000*rate, HAIlb=1000*lower, HAIub=1000*upper) %>% 
  select(HAIrate, HAIlb, HAIub) %>%
  cbind(Surveillance_manuscript2_9_19,.)

##Add intervention variable to the data set
Surveillance_manuscript2_9_19<-Surveillance_manuscript2_9_19 %>% mutate(Intervention=(Week>Vertline))

#We add observations at the Vertline which differ only in Intervention value--this allows us to construct a line which depicts the immediate impact of the intervention at Week 13
Surveillance_manuscript2_9_19<-Surveillance_manuscript2_9_19 %>%add_row(Week=Vertline, Date1=as.Date("2020-07-06"), Intervention=FALSE, Ptdays=1000)
Surveillance_manuscript2_9_19<-Surveillance_manuscript2_9_19 %>%add_row(Week=Vertline, Date1=as.Date("2020-07-06"), Intervention=TRUE, Ptdays=1000)

#We make sure that R knows the Date1 variable is a date, not a string variable
Surveillance_manuscript2_9_19$Date1<-as.Date(Surveillance_manuscript2_9_19$Date1)

#Create a new week variable Week2 whose value is 0 at week 13.  Use of this variable in the regression ensures that, in the ITS regression, the p-value of the "Intervention" variable is a test of the significance between the predicted values of the response variable with and without the intervention.
Surveillance_manuscript2_9_19$Week2<-Surveillance_manuscript2_9_19$Week-13

#Creates a variable for the middle of the week; this helps when adding Harris County
Surveillance_manuscript2_9_19<-Surveillance_manuscript2_9_19 %>%
  mutate(Date=if_else(Date2==as.Date("2020-04-17"),as.Date(Date2)-1, as.Date(Date2)-2))

```


We plot HAI rates and proportion of positive tests with confidence intervals.

```{r plot}

#Plot Proportion of positives tests vs time
ggplot(Surveillance_manuscript2_9_19)+geom_point(mapping=aes(x=Week, y=percentagemean, size=Tested))+theme_light()+geom_vline(xintercept=Vertline-0.5, color="red")+geom_errorbar(aes(ymin=percentagelb, ymax=percentageub, x=Week), width=.2,) +ylab("Proportion of tests positive with 95% CIs")+theme(axis.text.x = element_text(angle=45, hjust = 1, size=6))+xlab("Week")+scale_x_continuous(breaks=2:22, labels = c("Apr 20","Apr 27", "May 4"," May 11", "May 18","May 25", "Jun 1","Jun 8","Jun 15","Jun 22", "Jun 29","Jul 6","Jul 13","Jul 20", "Jul 27", "Aug 3","Aug 10","Aug 17","Aug 24","Aug 31", "Sep 7"), minor_breaks = (NULL))


#Plot HAI vs time
ggplot(Surveillance_manuscript2_9_19)+geom_point(mapping=aes(x=Week, y=HAIrate, size=Ptdays))+theme_light()+geom_vline(xintercept=Vertline-0.5, color="red")+geom_errorbar(aes(ymin=HAIlb, ymax=HAIub, x=Week), width=.2,)+ylab("HAI rate per 1000 patient-days with 95% CIs")+theme(axis.text.x = element_text(angle=45, hjust = 1, size=6))+xlab("Week")+scale_x_continuous(breaks=2:22, labels = c("Apr 20","Apr 27", "May 4"," May 11", "May 18","May 25", "Jun 1","Jun 8","Jun 15","Jun 22", "Jun 29","Jul 6","Jul 13","Jul 20", "Jul 27", "Aug 3","Aug 10","Aug 17","Aug 24","Aug 31", "Sep 7"), minor_breaks = (NULL))

```


We see that the total number of positive tests is `sum(Surveillance_manuscript2_9_19$Positives, na.rm = TRUE)` out of a total `sum(Surveillance_manuscript2_9_19$Tested, na.rm = TRUE)` tested, for a test positive percentage of:
`sum(Surveillance_manuscript2_9_19$Positives, na.rm = TRUE)/sum(Surveillance_manuscript2_9_19$Tested, na.rm = TRUE)`


# Statistical tables and plots

## ITS 1

We create an initial model that incorporates week as a linear predictor, ignoring the intervention.  The following code does the analysis.  We see that this model is inadequate to explain the data we observed; this model was not included in the paper itself.

```{r its1}

#Runs logistic regression treating Week as linear predictor, ignoring intervention effect
logistic1<-glm(cbind(Positives,Tested-Positives) ~ Week, family = binomial, data=Surveillance_manuscript2_9_19)
summary(logistic1)
tablelogistic1<- tbl_regression(logistic1, exponentiate = TRUE) %>% gtsummary::as_flextable() 


#Add predicted percentages to data set:
Surveillance_manuscript2_9_19$percentageyhat1<-100*predict(logistic1, newdata=Surveillance_manuscript2_9_19, type="response")

#Plot
plotlogistic1<-ggplot(Surveillance_manuscript2_9_19)+geom_point(mapping=aes(x=Week, y=percentagemean, size=Tested))+theme_light()+geom_vline(xintercept=Vertline-0.5, color="red")+geom_errorbar(aes(ymin=percentagelb, ymax=percentageub, x=Week), width=.2,) +ylab("Proportion of tests positive with 95% CIs")+geom_line(mapping=aes(x=Week, y=percentageyhat1), color="blue")+theme(axis.text.x = element_text(angle=45, hjust = 1, size=6))+xlab("Week")+scale_x_continuous(breaks=2:22, labels = c("Apr 20","Apr 27", "May 4"," May 11", "May 18","May 25", "Jun 1","Jun 8","Jun 15","Jun 22", "Jun 29","Jul 6","Jul 13","Jul 20", "Jul 27", "Aug 3","Aug 10","Aug 17","Aug 24","Aug 31", "Sep 7"), minor_breaks = (NULL))

#Runs poisson regression treating Week as linear predictor, ignoring intervention effect
poisson1<-glm(HAI ~ Week, offset = log(Ptdays), family = poisson(link = "log"), data = Surveillance_manuscript2_9_19)
summary(poisson1)
tablepoisson1<-tbl_regression(poisson1, exponentiate = TRUE) %>% gtsummary::as_flextable()

#Add predicted rates to data set
Surveillance_manuscript2_9_19$HAIyhat1<-1000*(predict(poisson1, newdata=Surveillance_manuscript2_9_19, type="response"))/Surveillance_manuscript2_9_19$Ptdays

#Plot HAI vs time
plotpoisson1 <-ggplot(Surveillance_manuscript2_9_19)+geom_point(mapping=aes(x=Week, y=HAIrate, size=Ptdays))+theme_light()+geom_vline(xintercept=Vertline-0.5, color="red")+geom_errorbar(aes(ymin=HAIlb, ymax=HAIub, x=Week), width=.2,)+ylab("HAI rate per 1000 patient-days with 95% CIs")+geom_line(mapping=aes(x=Week, y=HAIyhat1), color="blue")+theme(axis.text.x = element_text(angle=45, hjust = 1, size=6))+xlab("Week")+scale_x_continuous(breaks=2:22, labels = c("Apr 20","Apr 27", "May 4"," May 11", "May 18","May 25", "Jun 1","Jun 8","Jun 15","Jun 22", "Jun 29","Jul 6","Jul 13","Jul 20", "Jul 27", "Aug 3","Aug 10","Aug 17","Aug 24","Aug 31", "Sep 7"), minor_breaks = (NULL))


```

When we look at the rate of positive testing, the regression is as follows.:

`r tablelogistic1`
&nbsp;  

The OR ratio in this table is comparing each week to the week prior.


We plot the results of the analysis below:

```{r echo=FALSE}
print(plotlogistic1)
```

While when we look at the HAI rate, the regression is as follows.:

`r tablepoisson1`

&nbsp;  
The IRR ratio in this table is comparing each week to the week prior.

We plot the results of the analysis below:

```{r echo=FALSE}
print(plotpoisson1)
```

## ITS 2


We create an initial model that incorporates intervention as a categorical predictor, ignoring the effect of Week.  Again, we see this model is inadequate to explain our data; accordingly, the results of this analysis are not included in the final paper.

```{r its2}

#Runs logistic regression treating intervention as linear predictor, ignoring week effect
logistic2<-glm(cbind(Positives,Tested-Positives) ~ Intervention, family = binomial, data=Surveillance_manuscript2_9_19)
summary(logistic2)
tablelogistic2<- tbl_regression(logistic2, exponentiate = TRUE) %>% gtsummary::as_flextable()


#Add predicted percentages to data set
Surveillance_manuscript2_9_19$percentageyhat2<-100*predict(logistic2, newdata=Surveillance_manuscript2_9_19, type="response")

#Plot
plotlogistic2<-ggplot(Surveillance_manuscript2_9_19)+geom_point(mapping=aes(x=Week, y=percentagemean, size=Tested))+theme_light()+geom_vline(xintercept=Vertline-0.5, color="red")+geom_errorbar(aes(ymin=percentagelb, ymax=percentageub, x=Week), width=.2,) +ylab("Proportion of tests positive with 95% CIs")+geom_line(mapping=aes(x=Week, y=percentageyhat2), color="blue")+theme(axis.text.x = element_text(angle=45, hjust = 1, size=6))+xlab("Week")+scale_x_continuous(breaks=2:22, labels = c("Apr 20","Apr 27", "May 4"," May 11", "May 18","May 25", "Jun 1","Jun 8","Jun 15","Jun 22", "Jun 29","Jul 6","Jul 13","Jul 20", "Jul 27", "Aug 3","Aug 10","Aug 17","Aug 24","Aug 31", "Sep 7"), minor_breaks = (NULL))

#Runs poisson regression treating intervention as linear predictor, ignoring week effect
poisson2<-glm(HAI ~ Intervention, offset = log(Ptdays), family = poisson(link = "log"), data = Surveillance_manuscript2_9_19)
summary(poisson2)
tablepoisson2<-tbl_regression(poisson2, exponentiate=TRUE)

#Add predicted rates to data set
Surveillance_manuscript2_9_19$HAIyhat2<-1000*predict(poisson2, newdata=Surveillance_manuscript2_9_19, type="response")/Surveillance_manuscript2_9_19$Ptdays

#Plot HAI vs time
plotpoisson2<-ggplot(Surveillance_manuscript2_9_19)+geom_point(mapping=aes(x=Week, y=HAIrate, size=Ptdays))+theme_light()+geom_vline(xintercept=Vertline-0.5, color="red")+geom_errorbar(aes(ymin=HAIlb, ymax=HAIub, x=Week), width=.2,)+ylab("HAI rate per 1000 patient-days with 95% CIs")+geom_line(mapping=aes(x=Week, y=HAIyhat2), color="blue")+theme(axis.text.x = element_text(angle=45, hjust = 1, size=6))+xlab("Week")+scale_x_continuous(breaks=2:22, labels = c("Apr 20","Apr 27", "May 4"," May 11", "May 18","May 25", "Jun 1","Jun 8","Jun 15","Jun 22", "Jun 29","Jul 6","Jul 13","Jul 20", "Jul 27", "Aug 3","Aug 10","Aug 17","Aug 24","Aug 31", "Sep 7"), minor_breaks = (NULL))


```

When we look at the rate of positive testing, the regression is as follows.:

`r tablelogistic2`
&nbsp;  

We plot the results of the analysis below:

```{r echo=FALSE}
print(plotlogistic2)
```

While when we look at the HAI rate, the regression is as follows.:

`r tablepoisson2`
&nbsp;  
We plot the results of the analysis below:

```{r echo=FALSE}
print(plotpoisson2)
```


## ITS 3 

We create an initial model that incorporates intervention and Week but does not include an interaction term.  That is to say, we assume that the slope of the trend line is the same pre-intervention and post-intervention, but assume that the intervention leads to an instantaneous change in the trend line itself without an effect on its slope.  This model is also inadequate to explain our data and is not included in the paper.

```{r its3}

#Runs logistic regression treating intervention and week as independent predictors
logistic3<-glm(cbind(Positives,Tested-Positives) ~ Intervention+Week, family = binomial, data=Surveillance_manuscript2_9_19)
summary(logistic3)
tablelogistic3<- tbl_regression(logistic3, exponentiate = TRUE) %>% gtsummary::as_flextable()


#Add predicted percentages to data set
Surveillance_manuscript2_9_19$percentageyhat3<-100*predict(logistic3, newdata=Surveillance_manuscript2_9_19, type="response")

#Plot
plotlogistic3<-ggplot(Surveillance_manuscript2_9_19)+geom_point(mapping=aes(x=Week, y=percentagemean, size=Tested))+theme_light()+geom_vline(xintercept=Vertline-0.5, color="red")+geom_errorbar(aes(ymin=percentagelb, ymax=percentageub, x=Week), width=.2,) +ylab("Proportion of tests positive with 95% CIs")+geom_line(mapping=aes(x=Week, y=percentageyhat3), color="blue")+theme(axis.text.x = element_text(angle=45, hjust = 1, size=6))+xlab("Week")+scale_x_continuous(breaks=2:22, labels = c("Apr 20","Apr 27", "May 4"," May 11", "May 18","May 25", "Jun 1","Jun 8","Jun 15","Jun 22", "Jun 29","Jul 6","Jul 13","Jul 20", "Jul 27", "Aug 3","Aug 10","Aug 17","Aug 24","Aug 31", "Sep 7"), minor_breaks = (NULL))

#Runs poisson regression treating intervention and week as independent predictors
poisson3<-glm(HAI ~ Intervention+Week, offset = log(Ptdays), family = poisson(link = "log"), data = Surveillance_manuscript2_9_19)
summary(poisson3)
tablepoisson3<- tbl_regression(poisson3, exponentiate = TRUE) %>% gtsummary::as_flextable()


#Add predicted rates to data set
Surveillance_manuscript2_9_19$HAIyhat3<-1000*predict(poisson3, newdata=Surveillance_manuscript2_9_19, type="response")/Surveillance_manuscript2_9_19$Ptdays

#Plot HAI vs time
plotpoisson3<-ggplot(Surveillance_manuscript2_9_19)+geom_point(mapping=aes(x=Week, y=HAIrate, size=Ptdays))+theme_light()+geom_vline(xintercept=Vertline-0.5, color="red")+geom_errorbar(aes(ymin=HAIlb, ymax=HAIub, x=Week), width=.2,)+ylab("HAI rate per 1000 patient-days with 95% CIs")+geom_line(mapping=aes(x=Week, y=HAIyhat3), color="blue")+theme(axis.text.x = element_text(angle=45, hjust = 1, size=6))+xlab("Week")+scale_x_continuous(breaks=2:22, labels = c("Apr 20","Apr 27", "May 4"," May 11", "May 18","May 25", "Jun 1","Jun 8","Jun 15","Jun 22", "Jun 29","Jul 6","Jul 13","Jul 20", "Jul 27", "Aug 3","Aug 10","Aug 17","Aug 24","Aug 31", "Sep 7"), minor_breaks = (NULL))


```

When we look at the rate of positive testing, the regression is as follows.:

`r tablelogistic3`
&nbsp;  

The odds ratio of *Week* in this table is comparing each week to the week prior.


We plot the results of the analysis below:

```{r echo=FALSE}
print(plotlogistic3)
```

While when we look at the HAI rate, the regression is as follows.:

`r tablepoisson3`

&nbsp;  
The IRR ratio of *Week* in this table is comparing each week to the week prior.

We plot the results of the analysis below:

```{r echo=FALSE}
print(plotpoisson3)
```

## ITS 4

We create an initial model that incorporates intervention and Week with an interaction term.  This is a model where the intervention is assumed to both have an instantaneous change on the outcome of interest, as well as a change in the slope of the trend line over time.  These models are the ones presented in the paper

```{r its4}

#Runs logistic regression treating intervention and week as predictors with an interaction term
logistic4<-glm(cbind(Positives,Tested-Positives) ~ Intervention*Week2, family = binomial, data=Surveillance_manuscript2_9_19)
summary(logistic4)
tablelogistic4<- tbl_regression(logistic4, exponentiate = TRUE) %>% gtsummary::as_flextable()

#Add predicted percentages to data set
Surveillance_manuscript2_9_19$percentageyhat4<-100*predict(logistic4, newdata=Surveillance_manuscript2_9_19, type="response")

#Plot
Fig1A<-ggplot(Surveillance_manuscript2_9_19)+geom_point(mapping=aes(x=Week, y=percentagemean, size=Tested))+theme_light()+geom_vline(xintercept=Vertline-0.5, color="red")+geom_errorbar(aes(ymin=percentagelb, ymax=percentageub, x=Week), width=.2,) +ylab("Percentage of HCP \ntests positive")+geom_line(mapping=aes(x=Week, y=percentageyhat4), color="blue")+labs(size = "# patients tested")+theme(axis.text.x = element_text(angle=45, hjust = 1, size=6))+xlab(NULL)+scale_x_continuous(breaks=2:22, labels = c("Apr 20","Apr 27", "May 4"," May 11", "May 18","May 25", "Jun 1","Jun 8","Jun 15","Jun 22", "Jun 29","Jul 6","Jul 13","Jul 20", "Jul 27", "Aug 3","Aug 10","Aug 17","Aug 24","Aug 31", "Sep 7"), minor_breaks = (NULL))+theme(legend.justification = c(0,0.5))+theme(axis.title.y = element_text(size = 10))+scale_size(range = c(1,3))
Fig1A
ggsave("Fig 1A 2020-9-19.tiff")


#Runs poisson regression treating intervention and week as predictors with an interaction
poisson4<-glm(HAI ~ Intervention*Week2, offset = log(Ptdays), family = poisson(link = "log"), data = Surveillance_manuscript2_9_19)
summary(poisson4)
tablepoisson4<- tbl_regression(poisson4, exponentiate = TRUE) %>% gtsummary::as_flextable()


#Add predicted rates to data set
Surveillance_manuscript2_9_19$HAIyhat4<-1000*predict(poisson4, newdata=Surveillance_manuscript2_9_19, type="response")/Surveillance_manuscript2_9_19$Ptdays

#Plot HAI vs time
Fig1B<-ggplot(Surveillance_manuscript2_9_19)+geom_point(mapping=aes(x=Week, y=HAIrate, size=Ptdays))+theme_light()+geom_vline(xintercept=Vertline-0.5, color="red")+geom_errorbar(aes(ymin=HAIlb, ymax=HAIub, x=Week), width=.2,)+ylab("HAI rate per\n1000 patient-days")+geom_line(mapping=aes(x=Week, y=HAIyhat4), color="blue")+theme(axis.text.x = element_text(angle=45, hjust = 1, size=6))+xlab("Week")+scale_x_continuous(breaks=2:22, labels = c("Apr 20","Apr 27", "May 4"," May 11", "May 18","May 25", "Jun 1","Jun 8","Jun 15","Jun 22", "Jun 29","Jul 6","Jul 13","Jul 20", "Jul 27", "Aug 3","Aug 10","Aug 17","Aug 24","Aug 31", "Sep 7"), minor_breaks = (NULL))+theme(legend.justification = c(0,0.5))+theme(axis.title.y = element_text(size = 10)) +scale_size(range = c(1,3))+labs(size = "Patient-days")
Fig1B
ggsave("Fig 1B 2020-9-19.tiff")

```

When we look at the rate of positive testing, the regression is as follows.:

`r tablelogistic4`
&nbsp;  

The odds ratio of *Week2* in this table is comparing each week to the week prior *before the intervention is implemented*.

The odds ratio of *Week2* * *Intevention* in this table compares the rate of week-by-week change *before the intervention is implemented* to the rate of change *after the intervention is implemented*.

While when we look at the HAI rate, the regression is as follows.:

`r tablepoisson4`

&nbsp;  
The IRR ratio of *Week* in this table is comparing each week to the week prior *before the intervention is implemented2*.

The IRR ratio of *Week2* * *Intevention* in this table compares the rate of week-by-week change *before the intervention is implemented* to the rate of change *after the intervention is implemented*.


We create a final plot which combines the plots above with HarriS County data.
``` {r}
#Import data from Harris County
Harrisdata <- read.table("Harris_data.csv", sep = ",", header = TRUE)
Harrisdata <- as.data.frame(Harrisdata)

## convert dates to R Date format
Harrisdata$Date <- as.Date(Harrisdata$Date, format = "%m / %d / %y")

## plot Fig2A
coef1 <- round(3780 / 22) ## to transform second y-axis

Fig2Av2<-ggplot(Harrisdata) + geom_point(data = Surveillance_manuscript2_9_19, mapping=aes(x=Date, y=percentagemean, size=Tested)) + 
  theme_light() + 
  geom_vline(xintercept=as.Date("07/05/2020", format = "%m / %d / %y", size = 1), color="red") +
  geom_errorbar(data = Surveillance_manuscript2_9_19, aes(ymin=percentagelb, ymax=percentageub, x=Date), width=.2, color = "#5A5656")  + 
  ylab("Percentage of HCP \ntests positive") + 
  geom_line(data = Surveillance_manuscript2_9_19, mapping=aes(x=Date, y=percentageyhat4), color="blue") + 
  labs(size = "# patients tested") +
  theme(legend.justification = c(0,0.5)) + 
  theme(axis.title.y = element_text(size = 10)) + 
  scale_size(range = c(1,3)) + 
  geom_bar(mapping=aes(x=Date, y = epicurve_Harris / coef1), stat = "identity", alpha = 0.2) + ## add Harris County data
  scale_y_continuous(
    name = "Percentage of HCP \ntests positive",
    sec.axis = sec_axis(~.*coef1, name="Daily COVID-19 cases\nin Harris County")) + ## add second y-axis
  theme(axis.title.x=element_blank())


## plot Fig2B
coef2 <- round(3780 / 7) ## to transform second y-axis

Fig2Bv2<-ggplot(Harrisdata) + 
  geom_point(data = Surveillance_manuscript2_9_19, mapping=aes(x=Date, y=HAIrate, size=Ptdays)) + 
  theme_light() + 
  geom_vline(xintercept=as.Date("07/05/2020", format = "%m / %d / %y", size = 1), color="red") +
  geom_errorbar(data = Surveillance_manuscript2_9_19, aes(ymin=HAIlb, ymax=HAIub, x=Date), width=.2) +
  geom_line(data = Surveillance_manuscript2_9_19, mapping=aes(x=Date, y=HAIyhat4), color="blue") + 
  geom_bar(mapping=aes(x=Date, y = epicurve_Harris / coef2), stat = "identity", alpha = 0.2) + ## add Harris County data
  scale_y_continuous(
    name = "HAI rate per\n1000 patient-days",
    sec.axis = sec_axis(~.*coef2, name="Daily COVID-19 cases\nin Harris County")) + ## add second y-axis
  theme(axis.title.x=element_blank()) +
  theme(axis.title.y = element_text(size = 10)) +scale_size(range = c(1,3)) +
  labs(size = "Patient-days") +
  theme(axis.text.x = element_text(angle=45, hjust = 1, size=6))

plot_grid(Fig2Av2, Fig2Bv2, ncol = 1, align = "v")




```



Finally, we list citations for the analyses run:


```{r citations}
citation()
citation("dplyr")
citation("readxl")
citation("epitools")
citation("ggplot2")
citation("cowplot")
citation("gtsummary")

citation("readr")
citation("knitr")
citation("reshape2")
citation("dplyr")
citation("scales")
citation("ggthemr")
citation("svglite")


```


